\rsec{Experience}
\begin{enumerate}[ ]
\work{Berkeley ParLab}{Aug 2012}{Now}

  Working on program synthesis at the Berkeley ParLab with Professor Bodik and several fellow students. Developed a couple of synthesizers targeting GreenArrays chips---very low-power, low-memory chips with a stack-based architecture. One synthesizer was written in Racket and used the Microsoft Z3 SMT solver; the other was written in Haskell and used a simple probabilistic search algorithm.

\work{MixRank}{Dec 2012}{Now}

  Working part-time at MixRank, a YC startup in San Francisco. MixRank is an intelligence tool for marketers---essentially a search engine for ads. I am developing a simple aggregation framework for incrementally updating certain metrics based on ad data from web crawlers. I am using Python and PostgreSQL.

\work{Ashima Arts}{May 2012}{Aug 2012}

  Over the summer, I worked on \texttt{gloc}, a utility for creating and linking modules for GLSL. I worked on the tool itself in OCaml. We compiled the tool to JavaScript with \texttt{js\_of\_ocaml} and I embedded it into a Google Chrome extension. I also wrote a small open-source OCaml library for working with semantic version numbers: \texttt{ocaml-semver}.

\work{Copilot Labs}{Sep 2011}{May 2012}

  During sophomore year, I worked part-time at Copilot, a startup targeting restaurants. Here, I did a bit of everything: backend work with Python and Django, frontend with jQuery and Raphael.js and even ops, setting up Jenkins CI. Towards the end, I wrote a simple classifier to group restaurant menu items into categories like ``entree'' or ``appetizer''.

\work{Guidewire}{May 2011}{Jul 2011}

  Guidewire is an enterprise software company producing software for insurance companies. I worked on the internal tools team and, along with another intern, developed a tool to monitor the company's servers. I used Gosu (a language very similar to Java) for the backend and monitoring daemon and jQuery UI for the frontend.
\end{enumerate}
