\rsec{Personal Projects}

\begin{enumerate}[ ]
\si{Semantic Diff}

I am working on a semantic diff and merge tool codenamed \texttt{cow}, written in Haskell. The idea is to treat code as data rather than text. Currently, \texttt{cow} can detect moved blocks of code even if the block was also modified. It also does scope analysis which lets it detect when variables get renamed. It can do normal diffs and three-way merges. Unfortunately, the performance of the underlying algorithms is too limiting too be used in practice, but I should resolve that issue shortly. <\url{http://jelv.is/cow}>

\si{TPL}

I designed my own dynamically typed programming language, TPL. The semantics are influenced by Self, JavaScript and Haskell and the syntax is very similar to Haskell's. It has some interesting features like ``laziness on demand'' (fine control over what gets evaluated) and an object system unified with the scoping system (giving you complete control over how variables are looked up). It also has some completely inane features like the ability to change operator precedence at runtime. <\url{http://jelv.is/tpl}>

\si{Prolog}

I wrote a simple Prolog interpreter in Haskell. The goal was to use it to introduce people to some intermediate Haskell concepts like the list monad, so I aimed for clarity and simplicity over performance or feature completeness. The actual Prolog logic is only 70 lines of code! <\url{http://github.com/TikhonJelvis/Simple-Prolog}>

\si{Life}

I wrote a simple app for John Conway's Game of Life. The main goal was to teach people about functional reactive programming (FRP). I used wxWidgets and the Reactive Banana library for Haskell. I also created a slide deck and gave a 20 minute presentation on FRP using code from this project. <\url{http://jelv.is/frp}> <\url{http://github.com/TikhonJelvis/Reactive-Life}>

\si{More} I have more projects at my website <\url{http://jelv.is/projects.html}> and on my GitHub account <\url{http://github.com/TikhonJelvis}>.

\end{enumerate}
